PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-05 docs/_tex/index.tex
'disc

\subsection{Big picture}\label{big-picture}

Climate change, global warming, alien and invasive species development,
coastal erosion, sealevel rise, while further impact coastal ecosystems
in the future \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
]{holon2018predictive}; \citealp{marquet2024global}}. The demand for
meaningful and efficient monitoring methods for these habitats has
therefore never been greater \citetext{\citealp[
]{muller2018satellite}; \citealp[
]{villalobos2023remote}; \citealp{oiry2021using}}. Employing traditional
sampling methods to monitor these ecosystems is time and
resource-intensive, and the findings are often difficult to scale up.
Earth observation methods can bridge this gap and meet the needs for
monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
The retrieval of Essential Biodiversity Variables (EBVs) and Essential
Ocean Variables (EOVs) through satellite observations is increasingly
common, enabling comprehensive monitoring of entire ecosystems over
extended time periods \citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}.

>>>>

\subsection{Application of the model}\label{application-of-the-model}

Climate change, global warming, alien and invasive species development,
coastal erosion, sealevel rise, while further impact coastal ecosystems
in the future \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
]{holon2018predictive}; \citealp{marquet2024global}}. The demand for
meaningful and efficient monitoring methods for these habitats has
therefore never been greater \citetext{\citealp[
]{muller2018satellite}; \citealp[
]{villalobos2023remote}; \citealp{oiry2021using}}. Employing traditional
sampling methods to monitor these ecosystems is time and
resource-intensive, and the findings are often difficult to scale up.
Earth observation methods can bridge this gap and meet the needs for
monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
The retrieval of Essential Biodiversity Variables (EBVs) and Essential
Ocean Variables (EOVs) through satellite observations is increasingly
common, enabling comprehensive monitoring of entire ecosystems over
extended time periods \citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
significance of monitoring waters, particularly in light of the Water
Framework Directive (WFD ; \citep{directive2000eu}), cannot be
overstated in environmental management and conservation efforts. The WFD
mandates the achievement and maintenance of ``good ecological status''
for all European waters, which necessitates a comprehensive
understanding and monitoring of aquatic ecosystems, including coastal
habitats like seagrass \citetext{\citealp[
]{foden2007angiosperms}; \citealp[
]{nordlund2024one}; \citealp{Zoffoli2021}}.

Effective and efficient monitoring tools are essential for identifying
the impacts of human activities and natural changes on these ecosystems.
Drones, with their capability for high-resolution, multispectral
imagery, provide a novel and powerful means to rapidly and accurately
acquire ground truth data. This data is critical for calibrating and
validating satellite remote sensing applications, thereby enhancing our
capacity to monitor vast coastal areas systematically under the WFD
framework. The integration of drone technology facilitates a scalable
approach to environmental surveillance, offering significant
advancements in the spatial and temporal resolution of data collection.
This, in turn, supports the directive's objectives by enabling more
informed and timely management decisions for the preservation and
restoration of aquatic ecosystems.

### 2024-03-05 index.qmd
preprint warning
save0403
'disc

title: Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

@@

## Big picture

Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, while further impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global]. The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using]. Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems. [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].

>>>>

title: PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

@@

## Application of the model

Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, while further impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global]. The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using]. Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems. [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020]. The significance of monitoring waters, particularly in light of the Water Framework Directive (WFD ; @directive2000eu), cannot be overstated in environmental management and conservation efforts. The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].

Effective and efficient monitoring tools are essential for identifying the impacts of human activities and natural changes on these ecosystems. Drones, with their capability for high-resolution, multispectral imagery, provide a novel and powerful means to rapidly and accurately acquire ground truth data (i.e. output of the model used in the present study). This data is critical for calibrating and validating satellite remote sensing applications, thereby enhancing our capacity to monitor vast coastal areas systematically under the WFD framework. The integration of drone technology facilitates a scalable approach to environmental surveillance, offering significant advancements in the spatial and temporal resolution of data collection. This, in turn, supports the directive's objectives by enabling more informed and timely management decisions for the preservation and restoration of aquatic ecosystems.
